Commutative character sheaves and geometric types for supercuspidal representations

### 2017-08-02 Geometric types.tex
Corrections to table of standard sheaves
Small changes to the tables on perverse sheaves

\begin{center}
\begin{spacing}{1.3}
\begin{tabular}{|l|l|}
\hline
$C_3$ & regular semisimple elements \\
$C_2$ & regular unipotent elements \\
$C_2^-$ & $\{-u : \mbox{ regular unipotent $u$}\}$ \\
$1$ & $\{1\}$ \\
$-1$ & $\{-1\}$ \\
\hline
\end{tabular}
\end{spacing}
\end{center}

@@

\begin{spacing}{1.3}
\[
\begin{array}{|l|l|ccccccc|}
\hline
\text{Perverse} & \text{Standard} & \multicolumn{7}{|c|}{\text{Trace of Frobenius values at conjugacy classes}} \\ \cline{3-9}
\text{Sheaf} & \text{Sheaves} & (\begin{smallmatrix}1 & 0\\ 0 & 1\end{smallmatrix}) & (\begin{smallmatrix}2 & 0\\ 0 & 2\end{smallmatrix}) & (\begin{smallmatrix}0 & 1\\ 2 & 0\end{smallmatrix})  & (\begin{smallmatrix}1 & 1\\ 0 & 1\end{smallmatrix})  & (\begin{smallmatrix}1 & 2\\ 0 & 1\end{smallmatrix}) & (\begin{smallmatrix}2 & 1\\ 0 & 2\end{smallmatrix})  & (\begin{smallmatrix}2 & 2\\ 0 & 2\end{smallmatrix}) \\
\hline
\IC(\mathbf{1}_{C_3})  &  \mathbf{1}_{C_3}[3]  & -1 & -1 & -1 & -1 & -1 & -1 & -1 \\
 \IC(\mathbf{1}_{C_2})  &  \mathbf{1}_{C_2}[2] \oplus \mathbf{1}_1[0]  & 1 & 0 & 0 & 1 & 1 & 0 & 0 \\
 \IC(\cs{E}_{C_2})  &  \cs{E}_{C_2}[2]  & 0 & 0 & 0 &  \sqrt{-3}  &  -\sqrt{-3} & 0 & 0 \\
 \IC(\mathbf{1}_{C_2^-})  &  \mathbf{1}_{C_2^-}[2] \oplus \mathbf{1}_{-1}[0]  & 0 & 1 & 0 & 0 & 0 & 1 & 1 \\
 \IC(\cs{E}_{C_2^-})  &  \cs{E}_{C_2^-}[2]  & 0 & 0 & 0 & 0 & 0 &   \sqrt{-3}  &   -\sqrt{-3}  \\
 \IC(\mathbf{1}_1)  &  \mathbf{1}_1[0]  & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
 \IC(\mathbf{1}_{-1})  &  \mathbf{1}_{-1}[0]  & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
\hline
\end{array}
\]
\end{spacing}

\vspace{0.1in}
\noindent Using the trace of Frobenius values, we find that the rational virtual equivariant Weil sheaf complex
\[
- \IC(\mathbf{1}_{C_3}) - \frac32 \IC(\mathbf{1}_{C_2}) + \frac12 \IC(\cs{E}_{C_2}) - \frac32 \IC(\mathbf{1}_{C_2^-}) - \frac12 \IC(\cs{E}_{C_2^-}) + \frac32 \IC(\mathbf{1}_1) + \frac32 \IC(\mathbf{1}_{-1})
\]
also geometrizes $\chi$.  Note that all seven character sheaves appear in this geometrization, even though we start just with a character.

>>>>

\begin{center}
\begin{spacing}{1.3}
\begin{tabular}{|l|l|}
\hline
$C_3$ & regular semisimple elements \\
$C_2$ & regular unipotent elements \\
$C_2^-$ & $\{-u : \mbox{ regular unipotent $u$}\}$ \\
$1$ & $\{1\}$ \\
$2$ & $\{2\}$ \\
\hline
\end{tabular}
\end{spacing}
\end{center}

@@

\begin{spacing}{1.3}
\[
\begin{array}{|l|l|ccccccc|}
\hline
\text{Perverse} & \text{Standard} & \multicolumn{7}{|c|}{\text{Trace of Frobenius values at conjugacy classes}} \\ \cline{3-9}
\text{Sheaf} & \text{Sheaves} & (\begin{smallmatrix}1 & 0\\ 0 & 1\end{smallmatrix}) & (\begin{smallmatrix}2 & 0\\ 0 & 2\end{smallmatrix}) & (\begin{smallmatrix}0 & 1\\ 2 & 0\end{smallmatrix})  & (\begin{smallmatrix}1 & 1\\ 0 & 1\end{smallmatrix})  & (\begin{smallmatrix}1 & 2\\ 0 & 1\end{smallmatrix}) & (\begin{smallmatrix}2 & 1\\ 0 & 2\end{smallmatrix})  & (\begin{smallmatrix}2 & 2\\ 0 & 2\end{smallmatrix}) \\
\hline
\IC(\mathbf{1}_{C_3})  &  \mathbf{1}_{\SL_2}[3]  & -1 & -1 & -1 & -1 & -1 & -1 & -1 \\
 \IC(\mathbf{1}_{C_2})  &  \mathbf{1}_{C_2}[2] \oplus \mathbf{1}_1[2]  & 1 & 0 & 0 & 1 & 1 & 0 & 0 \\
 \IC(\cs{E}_{C_2})  &  \cs{E}_{C_2}[2]  & 0 & 0 & 0 &  \sqrt{-3}  &  -\sqrt{-3} & 0 & 0 \\
 \IC(\mathbf{1}_{C_2^-})  &  \mathbf{1}_{C_2^-}[2] \oplus \mathbf{1}_{2}[2]  & 0 & 1 & 0 & 0 & 0 & 1 & 1 \\
 \IC(\cs{E}_{C_2^-})  &  \cs{E}_{C_2^-}[2]  & 0 & 0 & 0 & 0 & 0 &   \sqrt{-3}  &   -\sqrt{-3}  \\
 \IC(\mathbf{1}_1)  &  \mathbf{1}_1[0]  & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
 \IC(\mathbf{1}_{2})  &  \mathbf{1}_{2}[0]  & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
\hline
\end{array}
\]
\end{spacing}

\vspace{0.1in}
\noindent Using the trace of Frobenius values, we find that the rational virtual equivariant Weil sheaf complex
\[
- \IC(\mathbf{1}_{C_3}) - \frac32 \IC(\mathbf{1}_{C_2}) + \frac12 \IC(\cs{E}_{C_2}) - \frac32 \IC(\mathbf{1}_{C_2^-}) - \frac12 \IC(\cs{E}_{C_2^-}) + \frac32 \IC(\mathbf{1}_1) + \frac32 \IC(\mathbf{1}_{2})
\]
also geometrizes $\chi$.  Note that all seven character sheaves appear in this geometrization, even though we start just with a character.
